DNSKEY Management

### 2012-12-10 paper/paper.tex
Correct conclusion

\newcommand{\wbjp}{\textsuperscript{JP}}
\newcommand{\wbts}{\textsuperscript{TS}}

@@

\section{Conclusion\wbjp\wbts}
%TODO improve conclusion... :-D
We have exposed the administrative challenges that arise with DNSSEC: while being far from trivial, these issues are not insurmountable, especially with regard to the gained benefits, and the modifications required from the three R's to their interaction process finally only consists in adaptations to already existing communication channels.

@@

SWITCH's case study showed that the existing issues can at least be harnessed at a TLD level. While a wider adoption is required to see if the infrastructure can indeed scale, the foundations that have been lain seem ready to take on the challenge.

>>>>

\newcommand{\wbjp}{\textsuperscript{JP}}
\newcommand{\wbts}{\textsuperscript{TS}}
\newcommand{\wbjpts}{\textsuperscript{JP,TS}}

@@

\section{Conclusion\wbjpts}
We have exposed the administrative challenges that arise with DNSSEC:
while being far from trivial, these issues are not insurmountable,
especially with regard to the gained benefits. Further, the
modifications required from side the three Rs to their interaction
process finally only consists in adaptations of already existing
communication channels.

@@

SWITCH's case study showed that the existing issues can be harnessed
at least at a TLD level. While a wider adoption is required to see if
the infrastructure can indeed scale, the foundations that have been
lain seem ready to take on the challenge.
